CreateFiguresReview

### 2025-06-14 manuscript/ResponseReview1.tex

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{3}
\tightlist
\item
  Figure 2 caption:a. Please provide a reference for the statement
  beginning, ``Because the survival function\ldots{}''.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\alph{enumi}.}
\setcounter{enumi}{1}
\tightlist
\item
  I am confused by the sentence beginning: ``For example, the high
  hazard of \ldots{}''. Could you please provide some additional
  explanation or a reference for more details on this interpretation?
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{4}
\tightlist
\item
  Lines 156-166: Generally, survival probabilities are described as
  probabilities of remaining event-free up until a certain point, rather
  than the probability of an event occurring in the future. Some clarity
  in wording could be used here.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{5}
\tightlist
\item
  Please confirm that you have defined all acronyms, abbreviations, and
  functions at their first use in the text. E.g., please define WAIC,
  LOO, P(t), ca(t), SOA, CrI, among others.
\end{enumerate}
\end{quote}

@@

Response: We define all acronyms on their first mention in the revised
ms.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{6}
\tightlist
\item
  Section 3.1 could be condensed in the main paper (additional details
  could be included in the supplementary material if important). Also,
  please double check your definition of functional programming.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{7}
\tightlist
\item
  Table 2: It could be helpful to show an example of a trial where an
  event never occurs, to help the reader connect what is written in the
  text (line 325-327) to what appears in the table.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{8}
\tightlist
\item
  Figure 4: Why is there no bin 40?
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{9}
\tightlist
\item
  Line 423: The phrase ``early responses'' is confusing as it implies
  temporal ordering of the responses (i.e., early vs.~late trials). I'd
  suggest using ``fast response'' or ``rapid responses'', or some other
  phrase along those lines.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{10}
\tightlist
\item
  Is the discussion of reference and index coding (lines 457 -- 464)
  needed? In the introduction, the authors state that knowledge of
  regression is assumed so I am not sure this is necessary to include,
  but I defer to the authors' judgment.
\end{enumerate}
\end{quote}

@@

Response: Index coding is not used a lot in experimental psychology so
we included a short discussion.

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{11}
\tightlist
\item
  Figure 6: I only see one width of credible interval for each line on
  this plot--- please clarify if you are plotting 80\% or 95\% credible
  intervals.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{12}
\tightlist
\item
  Line 536: To me, ``subject-specific'' and ``marginal'' mean the
  opposite things. That is, subject-specific is an effect that is
  conditional on an individual while a ``marginal'' effect has been
  marginalized/averaged over individuals. Could you please clarify your
  use of these terms here?
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{13}
\tightlist
\item
  Lines 584-587: Since this is a tutorial paper, I'd suggest including
  explanations for why you make changes (a), (b), and (c).
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{14}
\tightlist
\item
  Line 659: What is a ``fully varying effects structure''? Please
  define/explain.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{15}
\tightlist
\item
  Line 832-833: Please provide a reference for the statement, ``However,
  they require much more data\ldots{}''.
\end{enumerate}
\end{quote}

@@

Response:

\begin{quote}
\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\setcounter{enumi}{16}
\tightlist
\item
  Github code: Instruction 2 of the README states ``open the
  reproducible\_workflow.Rproj'' -- I can't find this R project, should
  it be the ``Tutorial\_EHA.Rproj'' instead?
\end{enumerate}
\end{quote}

@@

Response:

\section{Reviewer: 3}\label{reviewer-3}

\begin{quote}
Comments to the Author This tutorial guides readers through how to
wrangle cognitive reaction time data and address research questions
pertaining to temporal dynamics of cognition using event history
analysis (EHA) and speed/accuracy tradeoff analysis (SAT). Models are
illustrated for hazard functions, and conditional accuracy functions. A
nice feature of this study is that each model is presented in both the
Bayesian and frequentist frameworks. Having both frameworks provides
side-by-side comparisons such as when the Bayesian framework might be
preferred (e.g., when models do not converge in the Frequentist
framework, which is common when modeling multilevel data). The tutorial
also includes a section on simulation and power analysis for planning
experiments. I believe this tutorial could eventually be a useful
contribution to fellow psychological scientists. However, in its current
state, it was difficult to follow/ make my way through (despite existing
expertise in EHA), and also difficult to understand what the main
contributions were above and beyond existing works. Additionally, it was
not clear why the discrete time framework was chosen. The temporal
granularity of reaction time data seems like it would be better suited
for a continuous time framework. Altogether, the tutorial covers
important concepts, but it would benefit from greater accuracy and
clearer definitions of key terms. Carefully removing redundancies,
getting to the tutorial section much quicker (currently not until pg.
17), and being more precise with explanations of technical jargon would
enhance its clarity and accuracy.
\end{quote}

@@

Response: We discuss the main contributions above and beyond existing
works on page x of the revised ms. We address the issue of treating time
as discrete or continuous on page x of the revised ms. We removed
redundancies and included more precise explanations of technical jargon.

\begin{quote}
Code for the tutorials: I went to the github page and found a folder for
each of the 4 tutorials, which included sub-folders for data, figures,
and tables. It took a minute for me to realize that the actual R code
for each tutorial was in the main folder, not within each sub-folder.
This may also be confusing to readers. Additionally, each of the 4
tutorials, along with their sub-tutorials are provided in separate .Rmd
files. There were several download steps needed to get all the
information. To me, this made the user experience tedious, and made the
tutorials seem disjointed from one another. The authors might consider a
more comprehensive single Rmd file that is neatly organized with an
interactive table of contents (in the knitted html file). To me, this
would make the experience much more enjoyable and useful for readers.
Given that this is a tutorial, it would also be nice if the the
RMarkdowns were somewhat more standalone e.g., by including a brief
description of what a life table is and how to interpret the plot.
\end{quote}

@@

Response: We explain the location of the files in the README file. We
included a brief description of a life table and how to interpret the
plot in the R Mardown tutorial files. A single download step is possible
by either cloning the project, or downloading the ZIP file.

\begin{quote}
Contribution of this tutorial: It wasn't clear to me as a reader what
the unique contribution is for this tutorial and what gaps in the
literature it fills beyond existing texts and tutorials. For example, is
this a tutorial that is meant to specifically focus on experimental
psychology cognitive task data -- and that this type of data has special
characteristics/associated research questions that necessitate their own
stand-alone tutorial? If so, it may be helpful to give more detail on
what these specific characteristics tend to be that may make it
different from the many other types of psychology data. Or, is this a
tutorial on discrete time survival analysis that is meant to be broadly
applicable to psychological scientists, and the cognitive reaction time
data is just for illustrative purposes. If so, then much less emphasis
should be placed on the specific data type and more emphasis should be
placed more broadly on types of psychological data/ research questions
this method could be applied to. I think the distinction makes a big
difference in the entire framing of the tutorial, and choosing one or
the other will make the tutorial content much easier for readers to
absorb.
\end{quote}

@@

Response: This is a tutorial specifically focused on Bayesian methods
and cognitive experimental psychology data, such as response times and
saccade latencies. Analyzing such event latencies with EHA can give
better answers about the time course of psychological processes compared
to (a) ANOVA on means and (b) currently popular quantile-based
distributional methods. Information about the time course of cognitive
processes is present in the detailed shape of the hazard function which
quantifies the moment-to-moment changes in behavioral performance, in
terms of the risk of response occurrence, and the accuracy of responses
emitted. EHA thus allows answering research questions about the onset of
psychological effects, about time-locking of effects to stimuli, and
about how the effect changes on multiple time scales, i.e., with the
passage of time within trials, across trials, across blocks within a
session, etc. Applying EHA also has implications for experimental
design, such as response deadlines, timer on trial onset, etc.

\begin{quote}
On page 7, it states that there are not tutorials aimed at psychological
time-to-event data. Yet, there are at least a few existing empirical
article examples with accompanying tutorials in psychology (listed
below), and arguably some of the popular textbooks are also geared
toward psychological scientists (e.g., Singer \& Willett). Similarly,
many of the textbooks contain code to accompany their text. Regardless,
even if those are not counted, I still think it will be beneficial for
readers if the authors can make a clear case for what is unique about
psychological time-to-event data that necessitates a stand alone
tutorial/ what gaps in the existing textbooks/empirical
articles/tutorials the present tutorial serves to fill.
\end{quote}

@@

Response: We believe a stand-alone tutorial for cognitive experimental
psychology is necessary because (a) psychologists are reluctant to
abandon ANOVA and switch to EHA/SAT for several reasons, (b) as far as
we know, none of the existing tutorials focuses on Bayesian methods.

\begin{quote}
Lougheed, J. P., Benson, L., Cole, P. M., \& Ram, N. (2019). Multilevel
survival analysis: Studying the timing of children's recurring
behaviors. Developmental Psychology, 55(1), 53.
\end{quote}

\begin{quote}
Elmer, T., van Duijn, M. A., Ram, N., \& Bringmann, L. F. (2023).
Modeling categorical time-to-event data: The example of social
interaction dynamics captured with event-contingent experience sampling
methods. Psychological Methods.
\end{quote}

\begin{quote}
Mills, M. (2011). The fundamentals of survival and event history
analysis. Introducing Survival Analysis and Event History Analysis.
London: SAGE Publications, 1-17.
\end{quote}

@@

Response: We included these references in the revised ms.

\begin{quote}
Organization of the tutorial:The current version of the tutorial is much
longer than a typical AMPPStutorial. There are a few possibilities for
dealing with this. First, it may be that the tutorial could be split
into 2, such as splitting into tutorials 1-3 and tutorial 4 on its own.
Another possibility is that the focus could be primarily on the Bayesian
models, and then leave the frequentist models for either a supplement,
or to only live in the RMarkdown. This possibility may also be
beneficial due to the model convergence issues with at least one of the
frequentist models (which is common with multilevel data and why many
psychological scientists are moving to the Bayesian framework). A third
possibility is that the overall tutorial text could be greatly
streamlined, with major cuts to both the introduction and the discussion
sections.
\end{quote}

@@

Response: We focus primarily on the Bayesian models in the revised ms.
We also made major cuts to both the introduction and the discussion
sections.

\begin{quote}
Clarity and accuracy: -There are several instances where jargon terms
and key concepts pertinent to survival analysis need to be defined
and/or described in slightly more detail than what is currently
provided. For example, clearer descriptions of censoring and risk sets
(plus what it means to be at risk) should be given in the introduction.
\end{quote}

@@

Response: We provide clear descriptions of censoring and risk sets on
page x of the revised ms.

\begin{quote}
Additionally, many key details, such as the EHA equations are relegated
to supplementary materials. In my opinion, any key information that
makes the tutorial more accessible and precise should not be in
supplementary materials.
\end{quote}

@@

Response: We placed the equations for h(t), S(t), and ca(t) in the
revised ms. on page x. The equations for P(t) are still in the
supplementary material.

\begin{quote}
There are many abbreviations that were difficult to follow. EHA is
arguably standard, but SAT (for speed/accuracy trade-off) is less
familiar, and may therefore benefit from not being an abbreviation.
Similarly referring to hazard function as h(t), conditional accuracy
function as c(t) was less clear than just saying hazard function and
conditional accuracy function.
\end{quote}

@@

Response: Although SAT is rather standard in cognitive experimental
psychology, we tried to limit the use of abbreviations in main body of
the revised ms.

\begin{quote}
It would be helpful if the research questions that can be addressed by
the methods presented are clearly presented in each section. I think
that currently they are getting lost in the tutorial.
\end{quote}

@@

Response:

\begin{quote}
There are several opportunities to describe the method more precisely.
For example, the discrete time hazard function gives a `conditional'
probability (pg. 9).
\end{quote}

@@

Response:

\begin{quote}
Additionally, it may be helpful to use more standard notations such as
h(t\_ij) to indicate the conditional probability that the event occurs
in bin j for individual i, given that the individual had not already
experienced the event in a previous time period (lines 159-160, pg. 9).
\end{quote}

@@

Response:

\begin{quote}
Similarly, the survival probability is the probability that the event
occurs after bin j, \emph{given that the individual lhas survived up
until bin j}.
\end{quote}

@@

Response:

\begin{quote}
Throughout the tutorial, reference to individuals in the notation is
missing.
\end{quote}

@@

Response: We added reference to individuals in the notation.

\begin{quote}
Another inaccuracy is that in the discrete time framework, it is not an
instantaneous likelihood (line 161, pg. 9).
\end{quote}

@@

Response: Indeed, only continuous-time hazard can be called an
instantaneous likelihood.

\begin{quote}
Introduction: -Section 1.1 -- I had a difficult time understanding this
section as the opening to the tutorial, and the last paragraph seemed
out of place/abrupt. felt too vague to be understandable as the opening
to the tutorial.
\end{quote}

@@

Response:

\begin{quote}
Given that the speed-accuracy tradeoff analysis is described as central
to this tutorial, it may benefit from being introduced earlier than pg.
7.
\end{quote}

@@

Response: We introduce SAT analysis already on page x in the revised ms.

\begin{quote}
It seems that comparing and contrasting Bayesian and frequentist methods
may be outside the scope of a tutorial (pg. 7)
\end{quote}

@@

Response: We agree and focus now on the Bayesian models in the revised
ms.

\begin{quote}
As mentioned above, tutorial 4 -- while related -- could potentially be
its own stand-alone tutorial.
\end{quote}

@@

Response: We decided to keep tutorial 4.

\begin{quote}
Censoring is a key component of survival analysis that is missing from
the introduction
\end{quote}

@@

Response:

\begin{quote}
It might be useful to indicate early on the distinctions between
multilevel data, single events, and recurring events -- and that this
particular tutorial is only focused on single events.
\end{quote}

@@

Response: We included the following text on page x of the revised ms.:
This tutorial deals with single-event analyses which focus on the time
until a single event occurs in a trial (e.g., a button press), with
repeated measures obtained for each individual. Recurrent event analysis
deals with multiple events that can happen repeatedly to the same
individual within a single observation period.

\begin{quote}
It's not clear why a discrete time framework is used given the granular
temporal resolution of reaction time data -- this would also mean that
the data would not need to be separated into bins. Most textbooks (e.g.,
Allison's) often indicate discrete time methods are common for temporal
scales such as months, years, or decades (not milliseconds). Clearer
justification for the discrete time framework and separating the data
into bins would be helpful.
\end{quote}

@@

Response:

\begin{quote}
Clearer description of the data would be helpful for readers (as well as
only having this description in one place in the tutorial to be more
concise). For example, on pg. 10 it is indicated that 200 trials of 1
experimental condition are simulated. Can the event occur at any time in
those 200 trials? If the event occurs in trial 150, do the remaining 50
trials still occur, or does the time series end for that person? How are
those extra trials after an event occurred handled in the data wrangling
and analysis. Can events occur more than once?
\end{quote}

@@

Response:

\begin{quote}
Section 2.2 (pg. 10, lines 168-169), if describing what `statisticians
and mathematical psychologists say', it would be helpful to provide
supporting references.
\end{quote}

@@

Response: We provide supporting references on page x of the revised ms.

\begin{quote}
The numbered list on pg. 11 contained jargon statements without
explanations. Suggest to simplify and keep the focus on the data you are
using and specific research questions you are using survival analysis as
a tool to address.
\end{quote}

Response: We removed the numbered list in the revised ms.

\begin{quote}
In section 2.3, suggest to lead with the data and research questions of
interest and then show how features of survival analysis make it a good
method to examine the research questions. I also felt that up until now,
the tutorial has been very confusing and hard to follow. It could be
that starting the tutorial at section 2.3 (with a few extra details
filled in), may be an alternative.
\end{quote}

Response: We follow the suggestion of this reviewer to start the
tutorial at section 2.3. That is, we immediately provide an example
experiment/data set with a descriptive analysis that illustrates the
benefits of applying EHA to psychological time-to-event data such as
response times and saccade latencies. This new example data set is taken
from Panis \& Schmidt (2022).

\begin{quote}
Again, section 2.3.1 (the majority of pg. 12) was unclear and difficult
to follow for someone who already has knowledge of survival analysis,
but not much familiarity with cognitive process/reaction time data.
\end{quote}

@@

Response:

### 2025-06-14 manuscript/ResponseReview1.tex

\begin{quote}
From what is written, I did not have a clear sense of how temporal
states of cognitive processes and theory development could occur (pg.
14, lines 231-29). These ideas and the research questions are scattered
in many places throughout the tutorial, and are not very
clear/straightforward. It may be helpful to locate them in just one
place in the tutorial and provide a clearer description to guide
readers. Similarly, the statement on pg. 14 (lines 238-239) felt rather
strong without any references, and also out of scope for a tutorial.
\end{quote}

@@

Response:

\begin{quote}
It wasn't clear how section 3.1 added value to the tutorial
\end{quote}

@@

Response:

\begin{quote}
Section 3.2 -- it would be helpful if there was clarification in the
text on when it would not be possible to include varying intercepts and
slopes (i.e., at least clarifying that random intercepts are a
requirement, but sometimes random slopes are removed based on model
convergence issues -- however, this also begs the question of whether a
model should even be presented if it does not converge when it includes
random slopes\ldots)
\end{quote}

@@

Response:

\begin{quote}
Additionally in section 3.2, the text on pg. 16 is vague and does not
give much detail to readers.
\end{quote}

@@

Response:

\begin{quote}
Overall, the introduction spans across 16 pages, which feels long even
for a standard empirical article, let alone a tutorial. As currently
written, I think many readers will get lost before even getting to the
tutorials section.
\end{quote}

@@

Response: We restructured and shortened the introduction.

\begin{quote}
Tutorials section: -Rather than only using h(t), and ca(t), suggest to
use hazard function and conditional accuracy function along with their
mathematical notation. Without having presented any equations, using
terms such as h(t) and ca(t) seems odd.
\end{quote}

@@

Response: We try to limit the number of abbreviations used in the main
body of the revised ms.

\begin{quote}
Similarly, P(t) is never defined for readers.
\end{quote}

@@

Response: P(t) is defined only in the supplementary material.

\begin{quote}
Section 4.1.1. -- it would be helpful to clarify that the risk set also
pertains to individuals (not just bins)
\end{quote}

@@

Response: We clarify this on page x of the revised ms.

\begin{quote}
The connection between trials and bins could be made clearer (this is in
reference to the text on pg. 18, but I think the clarity would need to
come earlier on in the tutorial when describing the data)
\end{quote}

@@

Response:

\begin{quote}
Comprehension of the text on pg. 18 would be enhanced if both right and
left censoring had been clearly introduced previously. Although left
censoring is probably unlikely in the reaction time data used in the
tutorial -- if it is the case that this tutorial is meant for broader
data types in psychology, left censoring would certainly be relevant to
many other use cases.
\end{quote}

@@

Response: We introduce types of censoring on page x of the revised ms.

\begin{quote}
Section 4.1.2 was a clearer data description than had been presented up
until that point in the tutorial. Again, it is suggested that the
manuscript/tutorial could be dramatically reduced in length if
information was more concisely but descriptively written in a single
place (e.g., data descriptions).
\end{quote}

@@

Response: We provide the information on data descriptions in a single
place (page x of the revised ms.).

\begin{quote}
Suggest to be more precise with the language on pg. 21 (line 355) --
which data are nested within participants? The trial data? The binned
data?
\end{quote}

@@

Response:

\begin{quote}
pg. 22 discusses warning messages and lets readers know these can be
ignored but does not give details as to why. Since this is a didactic
tutorial, it may be helpful to have at least some explanation as to why
the warning can be ignored.
\end{quote}

Response:

\begin{quote}
pg. 22 -- since this is a tutorial, it might also be helpful to unpack
in more detail the section about identifying individuals who may be
guessing etc -- especially since these are very important
considerations.
\end{quote}

@@

Response: We unpack in more detail how individuals can be identified
that may be guessing, or that do not perform the task as intended.

\begin{quote}
section 4.3.1 -- (line 451) it would be helpful if more details is given
on how to set the analysis time window. What counts as ``enough data''?
Given that this is a tutorial, these types of detail are critical for
readers to be able to implement the method in their own work
\end{quote}

@@

Response:

\begin{quote}
section 4.3.1 (line 453) -- more detail is needed on the cloglog link
function and how it differs from the more commonly known about logit
link.
\end{quote}

@@

Response:

\begin{quote}
section 4.3.1 (line 456) -- what goes into the decision about whether to
treat time as a categorical or continuous predictor?
\end{quote}

@@

Response:

\begin{quote}
section 4.3.3. -- it might be helpful to give a brief indicator up front
to readers about the rationale/purpose of fitting both M0i and M1i,
especially given that no interpretation is given for M0i. Similarly, it
would be helpful to give a bit more detail on the purpose of the
comparison of M0i and M1i (given that this is a didactic tutorial).
\end{quote}

@@

Response: We provide a brief description of the rationale of comparing
models M0i and M1i on page x of the revised ms.

\begin{quote}
section 4.3.6. -- same thing here -- since this is a tutorial, at least
brief details on what the purpose of this section is would be helpful.
It might also be helpful here to define what is meant by credible
interval so that more novice readers don't confuse it with a confidence
interval.
\end{quote}

@@

Response:

\begin{quote}
The text on pg. 35 (lines 567-574) seems too in-depth for a tutorial
\end{quote}

Response:

\begin{quote}
pg. 36 -- it would be helpful to give more detail on how to interpret
the logit-ca scale
\end{quote}

@@

Response:

\begin{quote}
section 4.7 -- as previously mentioned, it is possible that tutorial 4
could be a stand alone tutorial. If it's not though, more details are
needed up front to tell readers what the purpose is and why this is
useful.
\end{quote}

@@

Response:

\begin{quote}
Discussion section: The Discussion section would benefit from being
shortened (AMPPS guidelines indicate discussions should be a brief
summary of their contents rather than a general discussion).
\end{quote}

@@

Response: We shortened the discussion section.

\begin{quote}
is `how long' a component of survival analysis -- or is it more accurate
to say `whether and when psychological states occur'?
\end{quote}

Response: It is more accurate to say `whether and when' psychological
states occur. However, based on those results, we can deduce information
about how long a psychological state lasts within a trial.

\begin{quote}
pg. 47 (lines 753-761) -- I had a difficult time understanding this
section
\end{quote}

@@

Response: We rewrote this section.

\begin{quote}
section 5.5 -- unclear that the multi-state model is actually an example
where a multi-state model would be relevant\ldots{} (the conceptual
example given seems like it would be more linked to either a hidden
Markov model or recurring event survival model)
\end{quote}

@@

Response: We provide a better example in the revised ms.

\begin{quote}
Figures: -Figure 1 is difficult to follow. It is unclear how the means
are being calculated. For example, it seems like in examples 2 and 3,
the means between conditions should be different. I was also confused in
example 4 because the difference in probability between the two
conditions in time bin 2 seems tiny. I was also confused because it
still looked like there was a big difference in probability between the
two conditions at bin 5. Was bin 6 by chance what was meant instead of
bin 5? It also still looked like there were differences later on such as
in bin 7. Example 5 also left me confused. It looked to me like the
effect started at bin 4 and ended at bin 8. Clarification (and perhaps
simplifying) this figure would be useful.
\end{quote}

@@

Response:

\begin{quote}
The description for figure 2 is unclear, particularly with respect to
the contrasting knowledge that can be gained from the survival function
and hazard function
\end{quote}
